General purpose gene annotation using deep learning

### 2020-04-21 paper/main.tex
longer input length

We also used multiple techniques to improve the prediction quality after the training was done. One very effective way for genomes with larger genes was to input longer sequences during inference time than during training. This was done for all animal genomes except the invertebrates. The input sequences were up to 10 times larger, depending on species group and assembly quality. This also demonstrates ability of our model to generalize as it is able to make successful prediction on far longer sequences than it has ever seen. The sequence length during inference can be any of 20.000, 50.000, 100.000 or 200.000 and is determined by the species family(?). Families that tend to have longer genes get assigned longer sequences. For more implementation details on this see Section \ref{sec:longer} or the source code.

@@

\subsection{Longer Sequence Input}
\label{sec:longer}
Implementation detail:
If the N75 of a species is less than twice as high as the supposed sequence length it is lowered until either this criteria is met or a length of 50.000 is reached.

Table of species with their length.

>>>>

We also used multiple techniques to improve the prediction quality after the training was done. One very effective way for genomes with larger genes was to input longer sequences during inference time than during training. This was done for all animal genomes except the invertebrates. The input sequences were up to 10 times larger, depending on species group and assembly quality. This also demonstrates the ability of our model to generalize as it is able to make successful prediction on far longer sequences than it has ever seen. The sequence length during inference can be any of 20.000, 50.000, 100.000 or 200.000 and is determined by the phylogenetic class. The assignment was chosen to keep the average gene length roughly proportional to the length of the sequence input. For more implementation details on this see Section \ref{sec:longer} or the source code.

@@

\subsection{Longer Sequence Input}
\label{sec:longer}
\begin{table}[!t]
\processtable{Input Sequence Length by Animal Class\label{tab:input_lengths}} {
\begin{tabular}{@{}lll@{}}
\toprule Class & Input Length in bp\\
\midrule
Mammalia & 200.000 \\
Reptilia (excluding Aves) & 200.000 \\
Aves & 100.000 \\
Amphibia & 100.000 \\
Actinopterygii & 50.000 \\
Chondrichthyes & 50.000 \\
Actinistia & 50.000 \\
Ascidiacea & 20.000 \\
Insecta & 20.000 \\
\botrule
\end{tabular}}{{\it Note:} Input sequence length for each phylogenetic class present in our animal dataset. As a rule of thumb, we found the input length should be proportional to the average gene length of the class while staying in the interval [20.000, 200.000]. If the N75 of a specific species was less than twice as high as the supposed sequence length it was lowered until either this criteria as met or a length of 50.000 was reached. }
\end{table}
